The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-03 article.tex
Could use all 8 combinations of site and clock models
Add MBD params in table

The models we use in our model comparison are the four combinations
of two site models and two clock models. We use the JC69 site model, which
is the (generative and) simplest model and GTR, the site model with most
degrees of freedom. For the clock models, we use the strict clock model,
which is the (generative and) simplest clock model, and the RLN clock model.

@@

>>>>

The models we use in our model comparison are the four combinations
of two site models and two clock models. We use the JC69 site model, which
is the (generative and) simplest model and GTR, the site model with most
degrees of freedom. For the clock models, we use the strict clock model,
which is the (generative and) simplest clock model, and the RLN clock model.
\richel{Could also just be all site models and clock models = 8 models}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{ l | c | c | c | c   c   c | c }
    \hline
idx & $n_{taxa}$ & $f_{taxa}^{MB}$ & $\mu$ & MB regime & $n_{\nu}$ evts & $q$ & $\lambda$ \\
    \hline
    \hline
1 & 50 & 0 & 0 & many modest  & 8 & 1 / 8 & derive \\
2 & 50 & 0 & 0 & intermediate & 4 & 1 / 4 & derive \\
3 & 50 & 0 & 0 & few intense & 2 & 1 / 2 & derive \\
4 & 50 & 0 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
5 & 50 & 0 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
6 & 50 & 0 & 0.1 & few intense & 2 & 1 / 2 & derive \\
7 & 50 & 0 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
8 & 50 & 0 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
9 & 50 & 0 & 0.2 & few intense & 2 & 1 / 2 & derive \\
10 & 50 & 0 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
11 & 50 & 0.25 & 0 & intermediate & 4 & 1 / 4 & derive \\
12 & 50 & 0.25 & 0 & few intense & 2 & 1 / 2 & derive \\
13 & 50 & 0.25 & 0 & many modest  & 8 & 1 / 8 & derive \\
14 & 50 & 0.25 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
15 & 50 & 0.25 & 0.1 & few intense & 2 & 1 / 2 & derive \\
16 & 50 & 0.25 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
17 & 50 & 0.25 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
18 & 50 & 0.25 & 0.2 & few intense & 2 & 1 / 2 & derive \\
19 & 50 & 0.25 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
20 & 50 & 0.25 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
21 & 50 & 0.5 & 0 & few intense & 2 & 1 / 2 & derive \\
22 & 50 & 0.5 & 0 & many modest  & 8 & 1 / 8 & derive \\
23 & 50 & 0.5 & 0 & intermediate & 4 & 1 / 4 & derive \\
24 & 50 & 0.5 & 0.1 & few intense & 2 & 1 / 2 & derive \\
25 & 50 & 0.5 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
26 & 50 & 0.5 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
27 & 50 & 0.5 & 0.2 & few intense & 2 & 1 / 2 & derive \\
28 & 50 & 0.5 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
29 & 50 & 0.5 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
30 & 50 & 0.5 & 0.2 & few intense & 2 & 1 / 2 & derive \\
31 & 50 & 0.75 & 0 & many modest  & 8 & 1 / 8 & derive \\
32 & 50 & 0.75 & 0 & intermediate & 4 & 1 / 4 & derive \\
33 & 50 & 0.75 & 0 & few intense & 2 & 1 / 2 & derive \\
34 & 50 & 0.75 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
35 & 50 & 0.75 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
36 & 50 & 0.75 & 0.1 & few intense & 2 & 1 / 2 & derive \\
37 & 50 & 0.75 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
38 & 50 & 0.75 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
39 & 50 & 0.75 & 0.2 & few intense & 2 & 1 / 2 & derive \\
40 & 50 & 0.75 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
41 & 50 & 1 & 0 & intermediate & 4 & 1 / 4 & 0 \\
42 & 50 & 1 & 0 & few intense & 2 & 1 / 2 & 0 \\
43 & 50 & 1 & 0 & many modest  & 8 & 1 / 8 & 0 \\
44 & 50 & 1 & 0.1 & intermediate & 4 & 1 / 4 & 0 \\
45 & 50 & 1 & 0.1 & few intense & 2 & 1 / 2 & 0 \\
46 & 50 & 1 & 0.1 & many modest  & 8 & 1 / 8 & 0 \\
47 & 50 & 1 & 0.2 & intermediate & 4 & 1 / 4 & 0 \\
48 & 50 & 1 & 0.2 & few intense & 2 & 1 / 2 & 0 \\
49 & 50 & 1 & 0.2 & many modest  & 8 & 1 / 8 & 0 \\
50 & 50 & 1 & 0.2 & intermediate & 4 & 1 / 4 & 0 \\
    \hline
  \end{tabular}
  \caption{
    Overview of the MBD parameters 1/3. 
  }
  \label{table:mbd_parameters_1}
\end{table}

\begin{table}
  \centering 
  \begin{tabular}{ l | c | c | c | c   c   c | c }
    \hline
idx & $n_{taxa}$ & $f_{taxa}^{MB}$ & $\mu$ & MB regime & $n_{\nu}$ evts & $q$ & $\lambda$ \\
    \hline
    \hline
51 & 100 & 0 & 0 & few intense & 2 & 1 / 2 & derive \\
52 & 100 & 0 & 0 & many modest  & 8 & 1 / 8 & derive \\
53 & 100 & 0 & 0 & intermediate & 4 & 1 / 4 & derive \\
54 & 100 & 0 & 0.1 & few intense & 2 & 1 / 2 & derive \\
55 & 100 & 0 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
56 & 100 & 0 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
57 & 100 & 0 & 0.2 & few intense & 2 & 1 / 2 & derive \\
58 & 100 & 0 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
59 & 100 & 0 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
60 & 100 & 0 & 0.2 & few intense & 2 & 1 / 2 & derive \\
61 & 100 & 0.25 & 0 & many modest  & 8 & 1 / 8 & derive \\
62 & 100 & 0.25 & 0 & intermediate & 4 & 1 / 4 & derive \\
63 & 100 & 0.25 & 0 & few intense & 2 & 1 / 2 & derive \\
64 & 100 & 0.25 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
65 & 100 & 0.25 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
66 & 100 & 0.25 & 0.1 & few intense & 2 & 1 / 2 & derive \\
67 & 100 & 0.25 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
68 & 100 & 0.25 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
69 & 100 & 0.25 & 0.2 & few intense & 2 & 1 / 2 & derive \\
70 & 100 & 0.25 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
71 & 100 & 0.5 & 0 & intermediate & 4 & 1 / 4 & derive \\
72 & 100 & 0.5 & 0 & few intense & 2 & 1 / 2 & derive \\
73 & 100 & 0.5 & 0 & many modest  & 8 & 1 / 8 & derive \\
74 & 100 & 0.5 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
75 & 100 & 0.5 & 0.1 & few intense & 2 & 1 / 2 & derive \\
76 & 100 & 0.5 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
77 & 100 & 0.5 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
78 & 100 & 0.5 & 0.2 & few intense & 2 & 1 / 2 & derive \\
79 & 100 & 0.5 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
80 & 100 & 0.5 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
81 & 100 & 0.75 & 0 & few intense & 2 & 1 / 2 & derive \\
82 & 100 & 0.75 & 0 & many modest  & 8 & 1 / 8 & derive \\
83 & 100 & 0.75 & 0 & intermediate & 4 & 1 / 4 & derive \\
84 & 100 & 0.75 & 0.1 & few intense & 2 & 1 / 2 & derive \\
85 & 100 & 0.75 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
86 & 100 & 0.75 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
87 & 100 & 0.75 & 0.2 & few intense & 2 & 1 / 2 & derive \\
88 & 100 & 0.75 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
89 & 100 & 0.75 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
90 & 100 & 0.75 & 0.2 & few intense & 2 & 1 / 2 & derive \\
91 & 100 & 1 & 0 & many modest  & 8 & 1 / 8 & 0 \\
92 & 100 & 1 & 0 & intermediate & 4 & 1 / 4 & 0 \\
93 & 100 & 1 & 0 & few intense & 2 & 1 / 2 & 0 \\
94 & 100 & 1 & 0.1 & many modest  & 8 & 1 / 8 & 0 \\
95 & 100 & 1 & 0.1 & intermediate & 4 & 1 / 4 & 0 \\
96 & 100 & 1 & 0.1 & few intense & 2 & 1 / 2 & 0 \\
97 & 100 & 1 & 0.2 & many modest  & 8 & 1 / 8 & 0 \\
98 & 100 & 1 & 0.2 & intermediate & 4 & 1 / 4 & 0 \\
99 & 100 & 1 & 0.2 & few intense & 2 & 1 / 2 & 0 \\
100 & 200 & 1 & 0.2 & many modest  & 8 & 1 / 8 & 0 \\
    \hline
  \end{tabular}
  \caption{
    Overview of the MBD parameters 2/3. 
  }
  \label{table:mbd_parameters_2}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{ l | c | c | c | c   c   c | c }
    \hline
idx & $n_{taxa}$ & $f_{taxa}^{MB}$ & $\mu$ & MB regime & $n_{\nu}$ evts & $q$ & $\lambda$ \\
    \hline
    \hline
101 & 200 & 0 & 0 & intermediate & 4 & 1 / 4 & derive \\
102 & 200 & 0 & 0 & few intense & 2 & 1 / 2 & derive \\
103 & 200 & 0 & 0 & many modest  & 8 & 1 / 8 & derive \\
104 & 200 & 0 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
105 & 200 & 0 & 0.1 & few intense & 2 & 1 / 2 & derive \\
106 & 200 & 0 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
107 & 200 & 0 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
108 & 200 & 0 & 0.2 & few intense & 2 & 1 / 2 & derive \\
109 & 200 & 0 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
110 & 200 & 0 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
111 & 200 & 0.25 & 0 & few intense & 2 & 1 / 2 & derive \\
112 & 200 & 0.25 & 0 & many modest  & 8 & 1 / 8 & derive \\
113 & 200 & 0.25 & 0 & intermediate & 4 & 1 / 4 & derive \\
114 & 200 & 0.25 & 0.1 & few intense & 2 & 1 / 2 & derive \\
115 & 200 & 0.25 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
116 & 200 & 0.25 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
117 & 200 & 0.25 & 0.2 & few intense & 2 & 1 / 2 & derive \\
118 & 200 & 0.25 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
119 & 200 & 0.25 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
120 & 200 & 0.25 & 0.2 & few intense & 2 & 1 / 2 & derive \\
121 & 200 & 0.5 & 0 & many modest  & 8 & 1 / 8 & derive \\
122 & 200 & 0.5 & 0 & intermediate & 4 & 1 / 4 & derive \\
123 & 200 & 0.5 & 0 & few intense & 2 & 1 / 2 & derive \\
124 & 200 & 0.5 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
125 & 200 & 0.5 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
126 & 200 & 0.5 & 0.1 & few intense & 2 & 1 / 2 & derive \\
127 & 200 & 0.5 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
128 & 200 & 0.5 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
129 & 200 & 0.5 & 0.2 & few intense & 2 & 1 / 2 & derive \\
130 & 200 & 0.5 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
131 & 200 & 0.75 & 0 & intermediate & 4 & 1 / 4 & derive \\
132 & 200 & 0.75 & 0 & few intense & 2 & 1 / 2 & derive \\
133 & 200 & 0.75 & 0 & many modest  & 8 & 1 / 8 & derive \\
134 & 200 & 0.75 & 0.1 & intermediate & 4 & 1 / 4 & derive \\
135 & 200 & 0.75 & 0.1 & few intense & 2 & 1 / 2 & derive \\
136 & 200 & 0.75 & 0.1 & many modest  & 8 & 1 / 8 & derive \\
137 & 200 & 0.75 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
138 & 200 & 0.75 & 0.2 & few intense & 2 & 1 / 2 & derive \\
139 & 200 & 0.75 & 0.2 & many modest  & 8 & 1 / 8 & derive \\
140 & 200 & 0.75 & 0.2 & intermediate & 4 & 1 / 4 & derive \\
141 & 200 & 1 & 0 & few intense & 2 & 1 / 2 & 0 \\
142 & 200 & 1 & 0 & many modest  & 8 & 1 / 8 & 0 \\
143 & 200 & 1 & 0 & intermediate & 4 & 1 / 4 & 0 \\
144 & 200 & 1 & 0.1 & few intense & 2 & 1 / 2 & 0 \\
145 & 200 & 1 & 0.1 & many modest  & 8 & 1 / 8 & 0 \\
146 & 200 & 1 & 0.1 & intermediate & 4 & 1 / 4 & 0 \\
147 & 200 & 1 & 0.2 & few intense & 2 & 1 / 2 & 0 \\
148 & 200 & 1 & 0.2 & many modest  & 8 & 1 / 8 & 0 \\
149 & 200 & 1 & 0.2 & intermediate & 4 & 1 / 4 & 0 \\
150 & 200 & 1 & 0.2 & few intense & 2 & 1 / 2 & 0 \\
    \hline
  \end{tabular}
  \caption{
    Overview of the MBD parameters 3/3. 
  }
  \label{table:mbd_parameters_3}
\end{table}
